Self-test prime dimensional EPR pairs with constant alphabet

### 2019-01-29 Draft/draft.tex
Honghao: added definitions and strengthened proposition 12

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
We use $[n]$ to denote the set $\{0,1 \dots n-1\}$ and $[n]+1$ for the set $\{1,2 \dots n\}$.
%We denote the group commutator of $A$ and $B$, i.e. $ABA^{-1}B^{-1}$, by $[A,B]$.
The EPR pair of local dimension $d$ for $d \geq 2$ is the maximally entangled state and is denoted by
\begin{align}
\ket{\EPR{d}} = \frac{1}{\sqrt{d}} \sum_{i = 0}^{d-1} \ket{ii}.
\end{align}
The superscript $(d)$ stresses the local dimension and we follow this convention through this paper.

We self-test $\ket{\EPR{d}}$ by verify that Alice and Bob has operators 
which have operators of the similar form
\begin{align}
	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/2}{k},
\end{align}
where $\omega_d = e^{i2\pi/d}$ is the primitive $d$th root of unity.
Through out this paper, any operation on the label of the eigenvector $k$ is taken modulo $d$,
unless otherwise specified, for example, the $i/2$ above.

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
The weighted CHSH inequality is given below 
\begin{align}
	\label{eq:chsh_op}
	\I_\alpha = \alpha\ip{A_0B_0}+\alpha\ip{A_0B_1} + \ip{A_1B_0} - \ip{A_1B_1}\leq 2\alpha,
\end{align}
where $A_x,B_y$ for $x,y = 0,1$ are Binary observables on Hilbert space $\calH_A$ and $\calH_B$ respectively.
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
the weighted CHSH inequality.
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
 \I_\alpha \leq 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy for $\I_\alpha$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_0 = \pauliz$, $A_1 = \paulix$,
	$B_0 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_1 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
We take an approach introduced in Ref.~\cite{bamps2015} and prove the following robust self-testing result.
\begin{theorem}
\label{thm:selftest}
	Suppose the quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the violation
	at least $2\sqrt{1+\alpha^2} - \epsilon$
	for some $\epsilon$, then
	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
	\begin{align}
		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{aux} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O(\sqrt{\epsilon})
	\end{align}
	for $x,y \in \{-1, 0, 1\}$ where the subscript $-1$ refers to the identity operator and $A_x, B_y$ are 
	defined in \cref{def:ideal}.
\end{theorem}
We defer the proof of \cref{thm:selftest} till Appendix~\ref{sec:selftest}.
After proving the robust self-testing result, we take one step further and observe an interesting property of the 
observable $\tilde{B}_0\tilde{B}_1$.
\begin{proposition}
\label{prop:2d-subspace}
	Suppose a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the maximal 
	violation of  $\I_{\cot(-\pi/2d)}$, then there exists a $2$-dimensional Hilbert space which is spanned by eigenvectors of 
	$\tilde{B}_0\tilde{B}_1$ of eigenvalue $\omega_d$ and $\omega_d^{-1}$.
\end{proposition}
\begin{proof}[Proof of \cref{prop:2d-subspace}]
	By \cref{thm:selftest}, the condition that the strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the  
	maximal value of $\I_{\cot(-\pi/2d)} $ implies that there exist states $\ket{u_0}, \ket{u_1} \in \supp(\Tr_A(\ketbra{\tpsi}{\tpsi}))$ such that 
	\begin{align*}
	(\tilde{B}_0 + \tilde{B}_1) \ket{u_0} = 2\cos(-\pi/2d) \ket{u_0} 
	&&(\tilde{B}_0 + \tilde{B}_1) \ket{u_1} = -2\cos(-\pi/2d) \ket{u_1}\\
	(\tilde{B}_0 - \tilde{B}_1) \ket{u_0} = 2\sin(-\pi/2d) \ket{u_1} 
	&&(\tilde{B}_0 - \tilde{B}_1) \ket{u_1} = 2\sin(-\pi/2d) \ket{u_0}.
	\end{align*}
	It is straightforward to calculate that 
	\begin{align*}
		\tilde{B}_0\tilde{B}_1 \ket{u_0} = \cos(\pi/d) \ket{u_0} -\sin(\pi/d) \ket{u_1},&&
		\tilde{B}_0\tilde{B}_1\ket{u_1} = \sin(\pi/d)\ket{u_0} + \cos(\pi/d) \ket{u_1},
	\end{align*}
	so we can conclude that 
	\begin{align*}
		&\tilde{B}_0\tilde{B}_1(\ket{u_0} + i\ket{u_1}) = e^{i \frac{\pi}{d}} (\ket{u_0} + i\ket{u_1}), &&
		&\tilde{B}_0\tilde{B}_1(\ket{u_0} - i\ket{u_1}) = e^{-i \frac{\pi}{d}} (\ket{u_0} - i\ket{u_1}).
	\end{align*}
	The actual eigenbasis we use is 
	\begin{align}
		\ket{x_1} = \frac{-1}{\sqrt{2}}(\ket{u_0} + i\ket{u_1}), &&
		\ket{x_{d-1}} = \frac{-e^{i\pi/2d}}{\sqrt{2}}(\ket{u_0} - i\ket{u_1})
	\end{align}
	so that 
	\begin{align}
		&B_0 = \omega_d\ketbra{x_1}{x_{d-1}} + \omega_d^{-1} \ketbra{x_{d-1}}{x_1},\\
		&B_1 =\ketbra{x_1}{x_{d-1}}  + \ketbra{x_{d-1}}{x_1},
	\end{align}
	which is important for the whole embedding argument to work in \cref{sec:comp}.
\end{proof}

@@

The quantum strategy of a game $G$ consists of projective measurements $\{\{A_x^a\}_a\}$ on Alice's side and 
$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$. Then the behaviour of Alice and Bob is described 
by the conditional probability
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
The \emph{value} of a strategy is given by
\begin{align}
	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
\end{align}

The main contribution of our work is the construction of a nonlocal game $\G$ with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
such that its optimal correlation can self-test $\ket{\EPR{d}}$ for arbitrary $d \in D$. 
The nonlocal game is a linear system game with modifications and strict enforcements. 
We introduce the definition of self-testing first and then the definition of linear system game, 
following definitions given in Ref.~\cite{coladan2017, slofstra2017}.
\begin{definition}[Self-testing]
	We say that a nonlocal game self-tests a quantum state $\ket{\Psi}$ if 
	any quantum strategy $S$ that achieves the optimal quantum value uses a shared state equivalent up to local isometry to $\ket{\Psi}$.
\end{definition}
\begin{definition}[Linear system game]
 Let $Hx = b$ be an $m \times n$ linear system over $\Z_2$. The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $1 \leq x \leq m$ and replies with $a \in \Z_2^{\times n}$,
 and Bob is given a variable number $y$ and replies with an assignment $b \in \Z_2$. The winning condition is 
 \begin{align*}
 	a(y) &= b && \text{(Consistency)} \\
	\sum_{y = 1}^n H_{xy} a(y) &\equiv b(x) \pmod 2. &&\text{(Constraint satisfaction)}
 \end{align*}
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.

@@

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
The goal of this section and the following two sections is to 
present a correlation that can self-test $\ket{\EPR{d-1}}$, 
where $d$ is prime and has primitive root $2$. 
If $d$ has primitive root $2$,
then $2$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$.
When $d$ is prime, $\Z_d^\times = \{1,2\dots d-1\}$.
The correlation we constructed is the optimal correlation for a game $\G$, which is the combination of two tests.
In this section, we introduce the linear system game which tests a relation that should be satisfied by 
Alice and Bob's observables.

Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$, which
is included in the group $K$, which has presentation
\begin{align*}
	K = \langle a,b,c,x,y: a^2=b^2=c^2 = e, c=ab, yay^{-1} = a, yby^{-1}= c, xyx^{-1} = y^2\rangle.
\end{align*}
The main component of $\G$ is a linear system game $\LS$, whose solution group is the embedding of the 
following group
\begin{align}
	\Pg= \langle u, x : uxu^{-1} = x^2 \rangle.
\end{align}

\begin{proposition}
	\label{prop:embed}
	The group $\Pg$ can be embedded into a linear system game, $\LS$, over $\Z_2$,
	with $118$ variables and $91$ equations, where each equation involves $3$ variables.
\end{proposition}
The process of embedding $\Pg$
into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Slofstra's seminal work \cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}..
\begin{proof}
The first step is to embed $\Pg$ into a linear-plus-conjugacy group $\Pg''$ where
all the generators are of order $2$, following the instructions given in the proof of  
Proposition~$4.8$ of the Ref.~\cite{slofstra2017}.
We first introduce $x_1,x_2$ such that $x_1^2=x_2^2=e$, $x=x_1x_2$ and $u x_2 u^{-1}=x_2$.
We also introduce $x' = ux_1u^{-1}$, 
then we embed $\Pg$ in $\Pg'$ as
\begin{align}
	\Pg' = \langle x_1,x_2,x',u: x_1^2=x_2^2=x'^2=e,
	x_1x_2x_1=x', ux_1u^{-1}=x', ux_2u^{-1} =x_2 \rangle.
\end{align}
Next, we introduce $u_1,u_2$ such that $u_1^2=u_2^2=e$ and $u=u_1u_2$, 
and also $u_3.u_4$ of order $2$ such that the conjugacy relations involving them are 
\begin{align*}
u_2x_2u_2 = u_3, && u_1u_3u_1 = x_2\\
u_2x_1u_2 = u_4, && u_1u_4u_1 = x',
\end{align*}
then
$\Pg'$ is further embedded in $\Pg''$ as
\begin{equation}
\begin{aligned}
	\Pg'' =  \langle &x_1,x_2,x',u_1,u_2,u_3,u_4: \text{all elements are of order $2$},\notag\\
	 &u_2x_2u_2 = u_3, u_1u_3u_1 = x_2,
u_2x_1u_2 = u_4, u_1u_4u_1 = x',x_1x_2x_1=x' \rangle.
\end{aligned}
\end{equation}	
To represent the conjugacy relations by a tuple, we relabel the some of the generators as
\begin{align*}
	u_1 = x_3, && u_2 = x_4, && x' = x_5, && u_3 = x_6, && u_4 = x_7,
\end{align*}
so that a simpler form of the group $\Pg''$ is 
\begin{equation}
\begin{aligned}
	\Pg'' = \langle \{x_i\}_{i=1}^7 : x_i^2 = e \; \forall i, 
	x_1x_2x_1=x_5, x_4x_2x_4 = x_6,
	 x_4x_1x_4=x_7, x_3x_2x_3 = x_6, x_3x_5x_3=x_7\rangle
\end{aligned}
\end{equation}
We collect the subscript of $x_i$'s in the conjugacy relations and define
\begin{align}
	C= \{ (1,2,5), (3,5,7), (4,1,7), (4,2,6), (3,2,6)\},
\end{align}
so that $(i,j,k) \in C$ if and only if $x_ix_jx_i = x_k$ in $\Pg''$.

Next we embed $\Pg''$ into $\Pg_{NLC}$ to make $x_j$ and $x_k$ commute if $(i,j,k) \in C$,
where $\Pg_{NLS}$ is a nice linear-plus-conjugacy group.
This steps are given in the proof of Lemma~$4.4$ of the Ref.~\cite{slofstra2017}.
The group $\Pg_{NLS}$ is defined as 
\begin{equation}
\begin{split}
\Pg_{NLS} = \langle \{x_i, w_i, y_i, j_i\}_{i=1}^{7},f : &f^2 = x_i^2 =w_i^2=y_i^2=j_i^2= e, \\
	&x_i = y_iz_i = fw_i,\; fy_if =z_i \quad\text{where } 1 \leq i \leq 7 \\
	&y_j z_k = z_ky_j,\; w_iy_jw_i = z_k \quad\text{for all } (i,j,k)\in C \rangle.
\end{split}
\end{equation}
To summarize the linear relations, we first introduce generator $g_{jk} = y_j z_k$ for all $(i,j,k) \in C$
such that $g_{jk}^2 = e$. Now the group has $34$ generator.
The $19$ linear relations are
\begin{align*}
	&x_i y_i z_i = e \quad \text{for} \quad i =1\dots 7 \\
	&x_i f w_i = e  \quad \text{for} \quad i =1\dots 7\\
	&g_{jk}y_jz_k =e \quad \text{for all}\quad (i,j,k) \in C.
\end{align*}
The $12$ conjugacy relations are 
\begin{align*}
	&fy_if = z_i\quad \text{for} \quad i =1\dots 7\\
	&w_iy_j w_i = z_k \quad\text{for all } (i,j,k)\in C.
\end{align*}
We can standardise the generators by relabeling the generators all as $x_i$.
There are $29$ generators in $\Pg_{NLS}$.

The last step is given in the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017}, which
embeds all the conjugacy relations in linear relations.
This is done by introduce $7$ new variables and $6$ linear relations for each
conjugacy relations. For example, If $I = (i,j,k)$ is a conjugacy relation, then we introduce
generators $y_{Ii}$ for $i=1 \dots 6$. Note that $y_{Ii}$ shall not be confused with the $y_i$'s
in the previous step. The new linear relations are
\begin{align*}
	x_i y_{I1} y_{I2} = e && x_j y_{I2} y_{I3} = e && y_{I3}y_{I4}y_{I5} = e\\
	x_i y_{I5} y_{I6} = e && x_k y_{I6} y_{I7} = e && y_{I1}y_{I4}y_{I7} = e.
\end{align*}
In the end, the solution group of $\LS$, $\Pg_{\LS}$,  
has $118$ variables and $91$ equations.
\end{proof}
In the later parts of the paper, we use $n = 118$ and $m = 91$ to refer to the size of $\LS$.
The key feature of this embedding is that $\LS$ has constant-sized input-output alphabet
even if the generators $u$ and $x$ can have arbitrary order.

We denote the special operators in the operator solution of $\LS$ that correpsond to generators 
$u = x_3x_4$ and $x = x_1x_2$ by $U$ and $S$.
The special property of $U$ and $S$ is summarized in the following lemma. 
\begin{lemma}
	\label{lm:ux_independ}
	Suppose there exist unitaries $U$ and $X$ which have the following forms
	\begin{align}
		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/2}{i},
	\end{align}
	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
\end{lemma}
Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^2$.
In the self-test proof, this lemma will be a critical step.
\begin{proof}
We are going to show the $(d-1)^2$ matrices from the set $\{U^k X^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1], l \in [d-1]+1}$
such that 
\begin{align}
	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
\end{align}
We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $2^{k_i} \equiv i \pmod{d}$.
The fact that $2$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.

@@

%=====================================
\section{Main result}
\label{sec:main}
%=====================================
In this section, we introduce the combined game $\G{d-1}$ and then
prove that it can self-test the state $\ket{\EPR{d-1}}$.

>>>>

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
We use $[n]$ to denote the set $\{0,1 \dots n-1\}$ and $[n]+1$ for the set $\{1,2 \dots n\}$.
%We denote the group commutator of $A$ and $B$, i.e. $ABA^{-1}B^{-1}$, by $[A,B]$.

We use some basic number theory concepts in our work. A primitive root of a prime number
$d$ is an integer $r$ such that $r \pmod{d}$ has multiplicative order $d-1$. Equivalently,
$r$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$ where
$\Z_d^\times = \{1,2\dots d-1\}$.
The EPR pair of local dimension $d-1$ for some prime $d$, which has primitive root $2$, 
is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{i = 0}^{d-2} \ket{ii}.
\end{align}
The superscript $(d-1)$ stresses the local dimension and we follow this convention through this paper.

We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
\begin{align}
	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/2}{k},
\end{align}
where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity.
Through out this paper, any operation on the label of the eigenvector $\ket{i}$ is taken modulo $d$,
unless otherwise specified, for example, the $i/2$ above.

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 0,1$ 
on Hilbert space $\calH_A$ and $\calH_B$ respectively.
A binary observable is a Hermitian matrix whose eigenvalues are either $+1$ or $-1$.
The weighted CHSH inequality is given by 
\begin{align}
	\label{eq:chsh_op}
	\I_\alpha = \alpha\ip{A_0B_0}+\alpha\ip{A_0B_1} + \ip{A_1B_0} - \ip{A_1B_1}\leq 2\alpha,
\end{align}
where $\ip{A_xB_y}$ is the expectation value of of the observables.
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
the weighted CHSH inequality.
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
 \I_\alpha \leq 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy for $\I_\alpha$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_0 = \pauliz$, $A_1 = \paulix$,
	$B_0 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_1 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
measurements, which is the phenomenon of self-test. We give formal statement of this self-test result in \cref{sec:chsh}.

@@

The quantum strategy of a game $G$ consists of projective measurements $\{\{A_x^a\}_a\}$ on Alice's side and 
$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$. Then the behaviour of Alice and Bob is described 
by the conditional probability
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
Note that we may use the term behaviour and correlation interchangeably.
The \emph{value} of a strategy is given by
\begin{align}
	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
\end{align}

The main contribution of our work is the construction of a correlation, which is the optimal correlation of a game $\G$ with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
such that this correlation can self-test $\ket{\EPR{d-1}}$ for arbitrary $d \in D$. 
The nonlocal game $\G$ is a linear system game with strict enforcements. 
We introduce the definition of self-testing first, the definition of linear system game, 
and its operator solution, 
following definitions given in Ref.~\cite{coladan2017, slofstra2017}.
\begin{definition}[Self-testing]
	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
	such that 	
	\begin{align*}
		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
	\end{align*}
\end{definition}
\begin{definition}[Linear system game]
 Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$ too. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = [m]+1$ and replies with $a \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = [n]+1$ and replies with an assignment $b \in \calB = \Z_2$. The winning condition is 
 that Alice's assignment to the variables should satisfy equation $i$ and Alice's $j$-th assignment $a(j)$ should match $b$.
 Formally, the winning condition is 
 \begin{align*}
 	a(j) &= b && \text{(Consistency)} \\
	\sum_{k= 1}^n H(i,k) a(k) &\equiv c(i) \pmod 2. &&\text{(Constraint satisfaction)},
 \end{align*}
 for all $(i,j) \in \calX \times \calY$.
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.
We focus on quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy for the linear system game $(Hx = c)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement, and
vice versa.

It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
operator solution in the following sense.
\begin{definition}[Operator solution of a linear system]
\label{def:op_sol}
	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of bounded Hermitian 
	operators $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that 
	\begin{enumerate}
		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
		\item for all $1 \leq i \leq m$,
		\begin{align*}
			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
		\end{align*}
	\end{enumerate}
	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
	solution in which the Hilbert space is finite-dimensional.
\end{definition}
Perfect quantum strategies can be extracted from operator solutions and vice versa.

Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
over $\Z_2$, which is called the solution group.
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,c) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
For concepts about group presentation, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
Combining \cref{def:op_sol} and \cref{def:presentation}, we know that an operator solution associated to $Hx =c$ is 
a finite-dimensional representation of $\Gamma(H,c)$ that maps $J$ to $-\1$.

@@

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
The goal of this section and the following two sections is to 
present a correlation that can self-test $\ket{\EPR{d-1}}$, 
where $d$ is prime and has primitive root $2$. 
The correlation we constructed is the optimal correlation for a game $\G$, which is the combination of two tests.
In this section, we introduce the linear system game which tests a relation that should be satisfied by 
Alice and Bob's observables.

Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.
The main component of $\G$ is a linear system game $\LS$, whose solution group is the embedding of the 
following group
\begin{align}
	\Pg= \langle u, x : uxu^{-1} = x^2 \rangle.
\end{align}
In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
relation $uxu^{-1} = x^2$.
\begin{proposition}
	\label{prop:embed}
	The group $\Pg$ can be embedded into a linear system game $\LS$ over $\Z_2$,
	with $118$ variables and $91$ equations, where each equation involves $3$ variables.
\end{proposition}
The process of embedding $\Pg$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Slofstra's seminal work \cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2}.

In the later parts of the paper, we use $n = 118$ and $m = 91$ to refer to the size of $\LS$.
The key feature of this embedding is that $\LS$ has constant-sized input-output alphabet
even if the generators $u$ and $x$ can have arbitrary order. 
We denote the special operators in the operator solution of $\LS$ that correpsond to generators 
$u = x_3x_4$ and $x = x_1x_2$ by $U$ and $X$.
The key relation that we will use in the later section is that 
\begin{align}
	(A_3A_4) (A_1A_2)(A_4A_3) \ket{\psi} = (A_1A_2)^2\ket{\psi}, 
\end{align}
where $\ket{\psi}$ is the state shared between Alice and Bob and $A_i$ is 
Alice's observable for $1 \leq i \leq n$.

The special property of $U$ and $X$ is summarized in the following lemma. 
\begin{lemma}
	\label{lm:ux_independ}
	Suppose there exist unitaries $U$ and $X$ which have the following forms
	\begin{align}
		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/2}{i},
	\end{align}
	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
\end{lemma}
Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^2$.
In the self-test proof, this lemma will be a critical step.
\begin{proof}
We are going to show the $(d-1)^2$ matrices from the set $\{U^k X^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1], l \in [d-1]+1}$
such that 
\begin{align}
	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
\end{align}
We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $2^{k_i} \equiv i \pmod{d}$.
The fact that $2$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.

@@

%=====================================
\section{Main result}
\label{sec:main}
%=====================================
In this section, we introduce the combined game $\G$ and then
prove that it can self-test the state $\ket{\EPR{d-1}}$.
